\cvsection{Experience}
\begin{cventries}
  \cventry
    {Data Team Software Engineer}
    {Razorfish}
    {\toronto}
    {May 2016 - PRESENT}
    {
      \begin{cvitems}
        \item {Created back end infrastructure to support product catalog data for Walmart.ca}
        \item {Maintained legacy data infrastructure built on Akka and Redis.}
        \item {Developed the next iteration of the data platform by scaling out with Scala, Akka, Cassandra, and Kafka.}
      \end{cvitems}
    }
  \cventry
    {Back End Software Engineer}
    {EnerNOC}
    {\vancouver}
    {June 2015 - April 2016}
    {
      \begin{cvitems}
        \item {Created several enterprise integration services in Scala using Akka, Spray, ScalikeJDBC and Postgres. Set up builds in SBT, and tested with ScalaTest and ScalaCheck. Spearheaded the adoption of Scala through teaching, establishing best coding practices, choosing libraries, overseeing intern projects, and leading study groups.}
        \item {Helped maintain the company's legacy Java Spring MVC app, and light front-end work for internal developer tools.}
      \end{cvitems}
    }
  \cventry
    {Full Stack Web Developer - Co-op Work Term 2}
    {Tipping Canoe}
    {\winnipeg}
    {January 2015 - April 2015}
    {
      \begin{cvitems}
        \item {Brought new features and bug fixes to multiple LAMP stack websites, using the Laravel PHP framework.}
        \item {Planned and developed database schema, along with migrations to accommodate changing requirements.}
        \item {Implemented front-end designs using Bootstrap, SASS, jQuery, and wrote JavaScript plugins for Redactor.}
      \end{cvitems} 
    }

  \cventry
    {Web Developer - Co-op Work Term 1}
    {iQmetrix}
    {\winnipeg}
    {May 2014 - August 2014}
    {
      \begin{cvitems}
        \item {Introduced Selenium web-browser integration testing in C\# to a large web application. Created features and fixed issues in web applications using ASP.NET, Marionette Backbone, and MEAN.js stack.}
      \end{cvitems}
    }
\end{cventries}
